More than one Author with different Affiliations

### 2016-01-14 manuscript.tex
added mean fst

Consistent with previous results \citep{hufford2012comparative}, we show that the maize SFS is skewed towards more intermediate-frequency variants (Figure \ref{fig:figure3}A-B), likely a result of the bottleneck associated with maize domestication \citep{Beissinger031666}.
We find further evidence of the effect of domestication using the Thetas method, revealing lower levels overall levels of diversity in maize (Figure \ref{fig:figure3}C). These results use Tripsacum as an ancestral sequence, which was generated using the Ancestral Sequence method in ANGSD-wrapper. %\jri{fill in \X's with which A-W script we used. probably need to modify this to mention Tripsacum and generation of the ancestral seq. and which A-W script we used for that.} done
Using the 2DSFS method, which includes an $F_{ST}$ calculation, we then scan our example region for windows with elevated differentiation between maize and teosinte. 
The mean $F_{ST}$ in this region is \X, close to the genome-wide reported value of \X \citep{hufford2012comparative}.\jri{change if not true}  
The \X windows in the 1\% tail of highest $F_{ST}$ values include genes several genes identified as potential targets of selection during domestication in \citep{hufford2012comparative} \jri{see supp tables in Huff. make supp. table of genes in top 1\%. sorry to add, but this is cool \& demonstrates more stuff A-W can do. don't need a graph}

>>>>

Consistent with previous results \citep{hufford2012comparative}, we show that the maize SFS is skewed towards more intermediate-frequency variants (Figure \ref{fig:figure3}A-B), likely a result of the bottleneck associated with maize domestication \citep{Beissinger031666}.
We find further evidence of the effect of domestication using the Thetas method, revealing lower levels overall levels of diversity in maize (Figure \ref{fig:figure3}C). These results use Tripsacum as an ancestral sequence, which was generated using the Ancestral Sequence method in ANGSD-wrapper. %\jri{fill in \X's with which A-W script we used. probably need to modify this to mention Tripsacum and generation of the ancestral seq. and which A-W script we used for that.} done
Using the 2DSFS method, which includes an $F_{ST}$ calculation, we then scan our example region for windows with elevated differentiation between maize and teosinte. 
The mean $F_{ST}$ in this region is 0.013, which is an order of magnitude lower than the genome-wide reported value of 0.11 \citep{hufford2012comparative}.   
The \X windows in the 1\% tail of highest $F_{ST}$ values include genes several genes identified as potential targets of selection during domestication in \citep{hufford2012comparative} \jri{see supp tables in Huff. make supp. table of genes in top 1\%. sorry to add, but this is cool \& demonstrates more stuff A-W can do. don't need a graph}
